A weakly structured stem for human origins in Africa

### 2023-02-27 paper.tex
accept suggestions

We used a subset of populations from the merged  sequencing data from the
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz}
and the Thousand Genomes Project (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} \sgcomment{This sounds like the Nama are from the 2015 paper. Perhaps: 
We generated a sequencing dataset by combining existing and newly recruited populations who are now part of the 
African Diversity Reference Panel (ADRP) \citep{Gurdasani2015-qy,Pagani2015-pz},
as well as Thousand Genomes Project populations (1KGP)
\citep{1000_Genomes_Project_Consortium2015-zq} 
}. These included the Amhara,
Bakiga, Gumuz, Nama, Oromo, Somali, and Zulu from ADRP, and ESN, GWD, LWK, MSL,
YRI, CEU, GBR, CHB, and PJL from 1KGP. After filtering for relatedness and
retaining Nama individuals with $>70\%$ estimated Khoe-San ancestry, we focused on
data from 289 individuals, including 44 Nama individuals. These were merged
with the high-coverage Neanderthal genome from Vindija Cave
\citep{Prufer2017-kk}. We kept variants from regions that fell within the 1KGP
srict callability mask, overlapped with at least 100 continuously called base
pairs in the Neanderthal genome, and were annotated as intergenic.
\texttt{ADMIXTURE} and PCA analyses were conducted on a subset of variants
filtered to remove variants in high LD ($r^2$ threshold of $0.1$). See SI
section \ref{sec:data-sequencing} for additional details on data and
sequencing.

>>>>

We generated a sequencing dataset by combining existing and newly recruited
populations who are now part of the African Diversity Reference Panel (ADRP)
\citep{Gurdasani2015-qy,Pagani2015-pz}, as well as Thousand Genomes Project
populations (1KGP) \citep{1000_Genomes_Project_Consortium2015-zq}. These
included the Amhara, Bakiga, Gumuz, Nama (newly generated), Oromo, Somali, and
Zulu from ADRP, and ESN, GWD, LWK, MSL, YRI, CEU, GBR, CHB, and PJL from 1KGP.
After filtering for relatedness and retaining Nama individuals with $>70\%$
estimated Khoe-San ancestry, we focused on data from 289 individuals, including
44 Nama individuals. These were merged with the high-coverage Neanderthal
genome from Vindija Cave \citep{Prufer2017-kk}. We kept variants from regions
that fell within the 1KGP srict callability mask, overlapped with at least 100
continuously called base pairs in the Neanderthal genome, and were annotated as
intergenic. \texttt{ADMIXTURE} and PCA analyses were conducted on a subset of
variants filtered to remove variants in high LD ($r^2$ threshold of $0.1$). See
SI section \ref{sec:data-sequencing} for additional details on data and
sequencing.
